Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce

### 2019-08-30 sample-sigchi.tex
update

%%
%% This is file `sample-sigchi.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigchi')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigchi.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigchi]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-9999-9/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Andrea Graziani}
\email{andrea.graziani93@outlook.it}
\affiliation{%
  \institution{Università Degli Studi di Roma Tor Vergata}
  \city{Rome}
  \state{Italy}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
MapReduce is often used to run critical jobs such as scientific data analysis. However, evidence in the literature shows that arbitrary faults do occur and can probably corrupt the results of MapReduce jobs; Moreover, ignoring data locality during task scheduling can lead to performance degradation and a pointless bigger network traffic.

@@

Although the execution of a job with our algorithms uses more resources respect to other implementations, like Hadoop, we believe that this cost is acceptable for critical applications that require that level of fault tolerance.

\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

@@

An important goal in distributed-systems design is to construct a system in such a way it can provide its services even in the presence of faults. In other words, whenever a failure
occurs, the system should continue to operate in an acceptable way; that is a distributed system is expected to be \textit{fault tolerant}. As known, many fault types exists in literature, the most serious of which are \textit{arbitrary failures}, also known as \textit{Byzantine failures}; whenever a that type of fault occurs, a server may produce arbitrary responses at arbitrary times which cannot be detected as being incorrect.

@@

\end{document}
\endinput
%%
%% End of file `sample-sigchi.tex'.

>>>>

\documentclass[sigchi]{acmart}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\acmConference[]{}{}{}
\acmBooktitle{}
\acmPrice{15.00}
\acmISBN{978-1-4503-9999-9/18/06}

\begin{document}

\title{Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce}

\author{Andrea Graziani}
\email{andrea.graziani93@outlook.it}
\affiliation{%
  \institution{Università Degli Studi di Roma Tor Vergata}
  \city{Rome}
  \state{Italy}
}

\renewcommand{\shortauthors}{Andrea Graziani (0273395)}

\begin{abstract}
MapReduce is often used to run critical jobs such as scientific data analysis. However, evidence in the literature shows that arbitrary faults do occur and can probably corrupt the results of MapReduce jobs; Moreover, ignoring data locality during task scheduling can lead to performance degradation and a pointless bigger network traffic.

@@

Although the execution of a job with our algorithms uses more resources respect to other implementations, like Hadoop, we believe that this cost is acceptable for critical applications that require that level of fault tolerance.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{MapReduce, Fault tolerance, Arbitrary failure, Data locality}

@@

Nowadays many famous distributed applications use thousands of computers and hundreds of other devices like network switches, routers and power units in order to provide their services to an increasing number of users in every part of the world.

Moreover there are various data-intensive task, like seismic simulation, natural language processing, machine learning, astronomical data parsing and web data mining, which require a processing power exceeds the capabilities of individual computers imposing the use of distributed computing. MapReduce, a framework developed by Google, represents a solution for processing large data sets.

As many studies confirm, \textit{hardware component failures are frequent} and they will probably happen more often in the future owing to the increasing number of computer and server connected to internet. Is been documented that in the first year of a cluster at Google there were 1000 individual machine failures and thousands of hard drive failures. A recent study of DRAM errors in a large number of servers in Google data-centres for 2.5 years concluded that these errors are more prevalent than previously believed, with more than 8\% DIMM affected by errors yearly, even if protected by error correcting codes (ECC) \cite{Abril07}. A Microsoft study of 1 million consumer PCs shown that CPU and core chipset faults are also frequent \cite{Abril07}

This is the reason why to construct a distributed system in such a way it can provide its services even in the presence of failures is become so critical for economic reasons; consequently, to provide a \textit{fault tolerant} cloud application represents an important goal in distributed-systems design.

As known academic literature describes many type of failure, like \textit{crash failures}; however the most serious are known as \textit{arbitrary failures} or \textit{Byzantine failures}, according to which a server may produce arbitrary responses at arbitrary times which cannot be detected as being incorrect.

Often mostly all data-intensive tasks require large data sets moving between computers in order to operate correctly. Moving data repeatedly to distant nodes is becoming the bottleneck [23].

Then the goal of this paper is to describe an Arbitrary Fault-Tolerant (AFT) MapReduce runtime system.

@@

\end{document}
\endinput
